\huge Tor's Usability for Censorship Circumvention

### 2016-04-14 pets2017-paper/pets2017-paper.tex
this fixes a weird page break error.

\subsection{Interacting Network Components} 
\label{sec:components}
Bridges, pluggable transports, and proxies are network components that 
circumvent censorship and interact with the Tor configuration interface. 
These components are shown in Fig.~\ref{fig:topology}.
Bridges and pluggable transports are completely Tor-specific concepts, whereas a proxy is not.  
This information is necessary to configure connections to Tor in censored environments.

@@

\begin{figure*}[t]
	\centering
		\includegraphics[width=.85\textwidth]{old-flow.pdf}
\hrule
		\includegraphics[width=1.0\textwidth]{new-flow.pdf} 
\caption{
Comparison of user flow in the ``OLD'' and ``NEW'' interfaces.
We collapsed the two bridge screens into one;
similarly the two proxy screens.
We swapped the order of the bridge and proxy configuration
so it matches the order of network components (Section~\ref{sec:components}).
We added a summary screen as a last step before initiating a connection.\\
\textbf{F}: first screen;
\textbf{B/B1/B2}: bridge screens;
\textbf{P/P1/P2}: proxy screens;
\textbf{S}: summary screen;
\textbf{Pr}: progress bar.
}
\label{fig:flow}
\end{figure*}

>>>>

\subsection{Interacting Network Components} 
Bridges, pluggable transports, and proxies are network components that 
circumvent censorship and interact with the Tor configuration interface. 
These components are shown in Fig.~\ref{fig:topology}.
Bridges and pluggable transports are completely Tor-specific concepts, whereas a proxy is not.  
This information is necessary to configure connections to Tor in censored environments.

@@

\begin{figure*}[t]
	\centering
		\includegraphics[width=.85\textwidth]{old-flow.pdf} 
		\caption{old flow} 
	\label{fig:old-flow}
\end{figure*}

\begin{figure*}[t]
	\centering
		\includegraphics[width=1.0\textwidth]{new-flow.pdf} 
		\caption{new flow} 
\end{figure*}
